---
title: "R Report - Allegheny County's Bureau of Weights and Measures"
author: "Marcelo Eduardo Redoschi"
date: "8/May/2021"
---

--- 
### Course: Unibz - Programming and Visualisation for Data Analytics - Programming for Data Analytics - Data Visualisation and Exploration  - 2020/21 - 73047A


*Continues from Part I, the Python notebooks, presented previously.*

---

```{r}
# 9 - 5 - 2021
## UNIBZ course: Programming and Visualisation for Data Analytics
## Data Visualisation and Exploration (Prof. Matteo Ceccarello)
# Author: "Marcelo Eduardo Redoschi"

library(tidyverse)
library(sf)
library(here)
# https://www.pasda.psu.edu/
# 
```

```{r, code = readLines("paths.R")}
source("paths.R")
```

#https://stackoverflow.com/questions/52397430/include-code-from-an-external-r-script-run-in-display-both-code-and-output
```{r, code = readLines("helper_functions.R")}
source("helper_functions.R")
```

```{r, code = readLines("stores.R")}
source("stores.R")
```

#### Maps 

```{r}
#pa_municipality_boundaries_url<-"ftp://ftp.pasda.psu.edu/pub/pasda/padot/boundary_layers/PaMunicipalities2021_03.zip"
pa_server_dir<-"ftp://ftp.pasda.psu.edu/pub/pasda/padot/boundary_layers"
pa_municipalities_fname<-'PaMunicipalities2021_03.zip'
pa_municipality_boundaries_url<-paste(pa_server_dir,pa_municipalities_fname,sep="/") 

pa_municipality_boundaries_zip_path<-file.path(maps_zip_dir, "PaMunicipalities2021_03.zip")
if (!file.exists(pa_municipality_boundaries_zip_path)) { 
  download.file(pa_municipality_boundaries_url, pa_municipality_boundaries_zip_path)
  unzip(pa_municipality_boundaries_zip_path, exdir=maps_dir)
}

pa_municipality_boundaries_shp_fname<-"PaMunicipalities2021_03.shp"
pa_municipality_boundaries_shp_path<-file.path(maps_dir,pa_municipality_boundaries_shp_fname)

```

```{r}
require(sf)


# ***** Jhub ***** 
if (grepl("jovyan", getwd(), fixed=TRUE)) { 

  pa_municipalities_shape <-st_read(pa_municipality_boundaries_shp_path)   

} else { 
  
# ***** Local machine *****

    pa_municipalities_shape <- here(pa_municipality_boundaries_shp_path) %>% 
    st_read()  
}
```


```{r}
pa_municipalities_shape
```

```{r}
pa_shape<-pa_municipalities_shape
municipalities_url<-"https://dced.pa.gov/wp-content/plugins/web-service/csv/municipalities.csv"
municipalities_path<-file.path(raw_dir, "pennsylvania_municipalities.csv")
if (!file.exists(municipalities_path)) 
  download.file(url=municipalities_url,destfile=municipalities_path)
```

```{r}
#ggplot(pa_municipalities_shape)+geom_sf()
```

####  Allegheny is of 67 counties in Pennsylvania.  

  
```{r}
allegheny_shape<-pa_municipalities_shape %>% filter(COUNTY=="02")
```

####  Within the county there are four administrative subdivisions: 
- Cities 
- Boroughs
- First townships
- Second Townships 

```{r}
ggplot(allegheny_shape)+geom_sf(aes(fill=CLASS_OF_M),color="black")+theme_minimal()+scale_fill_brewer(type = "div")
```
#### As observed above, the second townships may closely correspond with more rural areas. 

```{r}
allegheny_cities<-allegheny_shape %>% filter(CLASS_OF_M=="CITY")
```

```{r}
allegheny_cities$pop_density<-allegheny_cities$FIPS_MUN_P/allegheny_cities$FIPS_SQ_MI
city_centroids <- st_centroid(allegheny_cities)
city_centroids$pop_density<-city_centroids$FIPS_MUN_P/city_centroids$FIPS_SQ_MI/(2.5889)
ggplot(allegheny_cities)+geom_sf(aes(fill=MUNICIPAL1))+scale_fill_brewer(type="qual")+geom_sf(data=city_centroids,aes(size=pop_density))
```

```{r}
allegheny_rural<-allegheny_shape %>% filter(CLASS_OF_M=="2TWP")
```

```{r}
centroid <- st_centroid(allegheny_rural)
ggplot(allegheny_rural)+geom_sf()+geom_sf(data = centroid, color = 'red')
```